Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-15 cvpr2018.tex

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel method to deal with the challenging task of generating images conditioning on semantic image descriptions. We propose an effective end-to-end single-stream network that can generate photographic high-resolution images. Our method leverages deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics. We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions. 
We adopt a multi-purpose adversarial training strategy at multiple nested side outputs to encourage more effective image-text alignment in order to improve the semantic consistency and image fidelity simultaneously. Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images, thus alleviates the needs of human evaluation. 
With extensive experimental validation on three public datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics (e.g. a ${11.86}$ Inception score on COCO). 
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from one semantic text space to one complex RGB image space. This task requires the generated images to be not only realistic but also \textit{semantically consistent}, i.e., the generated images not only preserve object color and sketch in descriptions but also fine-grained descriptive details in image pixels. 
%However, this problem still remains unsolved due to its particular challenges. 
%insufficient methods are developed to successfully address this task due to its particular challenges.

@@

\begin{figure}[t]
%	\begin{center}
	\centering
	\begin{subfigure}[t]{0.5\textwidth}
	%	\centering
		\includegraphics[width=0.95\textwidth]{figure/intro2.pdf}
	\end{subfigure} \\
\centering
	\begin{subfigure}[t]{0.5\textwidth}
	%	\centering
		\includegraphics[width=0.95\textwidth,height=0.55\textwidth]{figure/single_view.pdf}
	\end{subfigure}
	\vspace{-.6cm}
	\caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two generated results where fine-grained details are highlighted. \label{fig:intro}} 	
	\vspace{-.6cm}
	%\end{center}
\end{figure}

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/intro.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/single_view.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only scale up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, StackGAN  \cite{han2017stackgan} propose a two-stage training strategy, which stacks another low-to-high resolution GAN to generate high-resolution $256^2$ images. Later on, \cite{dong2017semantic} proposes to bypass the difficult of learning mappings from vector embeddings to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}. It works by re-rendering an arbitrary-style $128^2$ training  image conditioned on a targeting description. However, its high-resolution synthesis capability remains unclear. 
At present, training a generative model to map from a low-dimensional text space to a high-resolution and diverse image space in a fully end-to-end manner still remains unsolved.

Text-to-image synthesis using GANs has two major difficulties. The first is balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}, which is actually a long-term problem in GANs. The second is stably modeling the huge pixel space in high-resolution images \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as guarantee semantic consistency.

%%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
%% Keeping semantic consistency as well as diversity
%%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these problems, in this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate semantically consistent and photographic image (see Figure \ref{fig:intro}). The contributions are described as follows.

Our generator resembles a simple vanilla GAN, without requiring any multiple internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints. 
We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution. 
We also propose a new convolutional neural network (CNN) for generator to support connections of discriminators at side outputs more effectively.
To guarantee the image diversity and semantic consistency,
we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches. 
%%\textcolor{red}{This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty.}%focal ranges

%To alleviate the need for manual human evaluation about the matching between generated images and text description, we propose to learn a visual-semantic embedding model, thus providing a measure for quantitative evaluation of the image sentence consistency.
%% It is a regularization to limit the discriminators to use unexpected information to make decision.

We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}. In complement of existing evaluation metric (inception score \cite{improvedGAN}) for generative models, we also introduce a new visual-semantic similarity metric to evaluate the alignment between generated images and conditioned text. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on three metrics. All source code will be released.

@@

Text-to-image synthesis is attractive problem in GANs. Reed \etal \cite{reed2016generative}  is the first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy for image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose generative
adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis. StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling images. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a CNN pretrained on ImageNet \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.

Learning a continuous mapping from a low-dimensional embedding manifold to a complex real data distribution is a long-standing problem. Although GANs have made significant progress, there are still many unsolved difficulties, e.g. training instability and high-resolution generation. Wide methods have been proposed to address the training instability, such as various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using extra knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}. \textit{While our method shows a new way to unite generators and discriminators and does not requires any extra knowledge apart from training paired text and images.} Additionally, it is easy to see the training difficulty increases significantly as targeting image resolution increases.

@@

To synthesize high-resolution images, cascade networks are effective to decompose originally difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
Denton \etal \cite{denton2015deep} train a cascade of GANs in a Laplacian pyramid framework (LAPGAN) and use each to synthesis details and push up the output resolution through by-stage refinement. StackGAN also shares some similar idea with LAPGAN. Inspired by this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps. 
%%Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear. 
Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for high-resolution image generation (Figure \ref{fig:archs-review} C). \textit{Compared with these strategies that train low-to-high resolution GANs progressively, our method has the advantages of leveraging mid-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. Particularly, using deep supervision \cite{lee2015deeply} in hierarchical convolutional layers can increase the discriminativeness of feature representations. 
\textit{Our hierarchically-nested adversarial objective is inspired by these families of deeply-supervised CNNs. }
%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.

@@

\subsection{Adversarial objective basics}
In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other. The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate fake images to fool the discriminator. Concretely, the overall min-max optimization objective is defined as: 
%where the optimal $G$ and $D$ can be obtained by 
%The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to fool the discriminator and transform an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by 
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{V}(D, G, Y, \bm z),
\end{split}
\end{equation}
where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise. The value function $\mathcal{V}$ aims to minimize the Jensen-Shannon divergence between the data and the model distribution. $G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$.

@@

\subsection{Hierarchical-nested adversarial objectives}
%Directly predicting high resolution synthesized images are challenging, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
Numerous methods have demonstrated ways to unite generators and discriminators for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
Our method actually explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features of the generator $\mathcal{G}$. 
The hierarchically-nested objectives 
%We conjecture that adding hierarchical adversarial objective using side outputs can
act as regularizers to the hidden space of $\mathcal{G}$, which can reduce the training instability and also offer a short path for better error signal flows.

The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4) with multiple side outputs:
%This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.  
\begin{equation}
\label{side}
X_1,..., X_s = \mathcal{G}(\bm t, \bm z), 
\end{equation}
where  $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution (generated by a text character encoder). $\mathcal{G}$ produces $s-1$ side outputs $\{X_1,...,X_{s-1}\}$ (resolution-growing images) and a final output $X_s$ with the highest resolution.

@@

For each $X_i$, we propose to apply a distinct discriminator $D_i$ to perform adversarial games independently. Therefore, our full min-max objective is defined as 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z), \\
  %\text{where} \;\;	 \mathcal{D} & =  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
\end{split}
\end{equation}
where $\mathcal{D}  =  \{D_1, ..., D_s\} $, and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ denotes a set of training images at multi-scales, $\{1,...,s\}$.
%where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
%Please note that in this setting, 
Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), which learns diverse discriminative features in different contextual scales, respectively.
%%Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.

In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details on these image structures. Since our method is able to be trained in an end-to-end fashion, the lower-resolution outputs can fully enjoy top-down knowledge from discriminators for higher resolutions, such that consistent image structures and styles appear in both low and high resolutions.
As an evidence, we can obtain significantly more consistent results exhibited in both low- and high-resolution outputs than StackGAN (see experiments). 
According to our empirical observation, our design is able to reduce the model instability, especially at the early stage of the training.
%% %We present the following multi-purpose adversarial loss to support more effective generator training.

\subsection{Multi-purpose adversarial losses}
Our generator produces size-growing side outputs which compose an image pyramid. 
We leverage this hierarchy property and allow adversarial losses to be multi-purpose to capture different (conditioned and unconditioned) statistics, with a goal to guarantee both semantic consistency and image fidelity.

To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}. The discriminator is designed to take image-text pairs as inputs and trained to identify two types of errors: real image with mismatched text and fake image with conditioned text.

The pair loss is designed to guarantee the global semantic consistency. However, there lacks an explicit loss that forces the discriminator to differentiate pure real images from fake images. Combining both tasks (generating realistic images and matching image styles with text) into one loss complicates the already challenging learning tasks. Moreover, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture the local fine-grained details.
%As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
%However, this loss has two major weaknesses. First, there is no explicit loss that force the discriminator to differentiate real images from fake images. 
%Combining both tasks (generating realistic images and matching image with text) into one output further complicates the learning tasks, which is already challenging. 
%Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.  
In addition, as pointed in \cite{shrivastava2016learning}, a single global discriminator may over-emphasize certain biased local features and lead to artifacts.

To guarantee the image fidelity, our solution is to add local adversarial image losses on image patches. 
%The insights are two folds:
%\begin{itemize}\vspace{-.1cm}
%\setlength\itemsep{-0.3em}
%\item Further forcing the generated samples to have only only global but also local similar statistics to real image patches, which is beneficial for rendering fine-grained details. 
%
%\item \textcolor{red}{Image loss without using paired text can be beneficial in the sense that it focus more on image information. The richness of discriminator supervision usually has advantages for generalization. } 
%\vspace{-.2cm}
%\end{itemize}
We expect the low-resolution discriminator to focus on global structures, while high-resolution outputs focus more on local image details. Through the pyramid of the size-growing side outputs, we configure the size of each image patch need to classify, termed  the focal range, to be adaptive.
The local image adversarial loss can be implemented as an fully CNN \cite{shrivastava2016learning,zhu2017unpaired}, and it is the second branch of our discriminator for the pair loss (see Section 3.4).
Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on generated image in the pyramid.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.49\textwidth]{figure/loss.pdf}
	\vspace{-.7cm}
	\caption{Given a set of images from the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to classify real or fake patches). The focal range decreases as the image size grows. }  \vspace{-.3cm}
	\label{fig:loss}
\end{figure}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel method to deal with the challenging task of generating photographic images conditioned on semantic image descriptions.
Our method introduces accompanying hierarchical-nested adversarial objectives inside the network hierarchies, which regularize mid-level representations and assist generator training to capture the complex image statistics. We present an extensile single-stream generator architecture to better adapt the jointed discriminators and push generated images up to high resolutions. We adopt a multi-purpose adversarial loss to encourage more effective image and text information usage in order to improve the semantic consistency and image fidelity simultaneously. Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images, which also alleviates the cost of human evaluation. With extensive experimental validation on three public datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics.

\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from a semantic text space to a complex RGB image space. This task requires the generated images to be not only realistic but also \textit{semantically consistent}, i.e., the generated images preserve the object color and sketch described in text and fine-grained descriptive details in image pixels as well.

%However, this problem still remains unsolved due to its particular challenges. 
%insufficient methods are developed to successfully address this task due to its particular challenges.

@@

\begin{figure}[t]
%	\begin{center}
	\centering
	\begin{subfigure}[t]{0.5\textwidth}
	%	\centering
		\includegraphics[width=0.95\textwidth]{figure/intro2.pdf}
	\end{subfigure} \\
\centering
	\begin{subfigure}[t]{0.5\textwidth}
	%	\centering
		\includegraphics[width=0.95\textwidth,height=0.55\textwidth]{figure/single_view.pdf}
	\end{subfigure}
	\vspace{-.6cm}
	\caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two generated results where fine-grained details are highlighted. \label{fig:intro}} 	
	\vspace{-.5cm}
	%\end{center}
\end{figure}

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/intro.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/single_view.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
Recently, generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only scale up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, StackGAN  \cite{han2017stackgan} is a successful approach, which stacks another low-to-high resolution GAN to generate high-resolution $256^2$ images in a two-stage training strategy. Later on, \cite{dong2017semantic} proposes to bypass the difficult of learning a mapping from text to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}. It works by re-rendering an arbitrary-style $128^2$ training  image conditioned on a targeting description. However, its high-resolution synthesis capability is still unclear. 
At present, training a generative model to map from a low-dimensional text space to a high-resolution image space in a fully end-to-end manner still remains unsolved.

This paper pays attention to two major difficulties for text-to-image synthesis using GANs. The first is balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}, which is actually a long-term problem in GANs. The second is stably modeling the huge pixel space in high-resolution images and guaranteeing semantic consistency \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to stabilize the training and help capture the complex image statistics \cite{huang2016stacked}.

In this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate semantically consistent and photographic images (see Figure \ref{fig:intro}). The contributions are described as follows.

Our generator resembles a simple vanilla GAN, without requiring any multiple internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional `deep' adversarial constraints. 
We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and jointly encourage the generator approaching the real training data distribution. 
We also propose a new convolutional neural network (CNN) design for the generator to support accompanied discriminators more effectively in an end-to-end training manner.
To guarantee the image diversity and semantic consistency,
we enforce discriminators at scale-different generator side outputs to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake
local image patches.

%%\textcolor{red}{This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty.}%focal ranges
%To alleviate the need for manual human evaluation about the matching between generated images and text description, we propose to learn a visual-semantic embedding model, thus providing a measure for quantitative evaluation of the image sentence consistency.
%% It is a regularization to limit the discriminators to use unexpected information to make decision.

We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}. In complement of existing evaluation metric (e.g. Inception score \cite{improvedGAN}) for generative models, we also introduce a new visual-semantic similarity metric to evaluate the alignment between generated images and conditioned text. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on three metrics.

All source code will be released.

@@

Text-to-image synthesis is a significant problem in GANs. Reed \etal \cite{reed2016generative}  is the first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy for image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose a generative
adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis. StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling images. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss \cite{johnson2016perceptual} with a CNN pretrained on ImageNet  and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.

Learning a continuous mapping from a low-dimensional embedding manifold to a complex real data distribution is a long-standing problem. Although GANs have made significant progress, there are still many unsolved difficulties, e.g. training instability and high-resolution generation. Wide methods have been proposed to address the training instability, such as various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using extra knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}. \textit{While our method shows a new way to unite generators and discriminators and does not requires any extra knowledge apart from training paired text and images.} Additionally, it is easy to see the training difficulty increases significantly as the targeting image resolution increases.

@@

To synthesize high-resolution images, cascade networks are effective to decompose originally difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
Denton \etal \cite{denton2015deep} train a cascade of GANs in a Laplacian pyramid framework (LAPGAN) and use each to synthesize and refine image details and push up the output resolution stage-by-stage. StackGAN also shares some similar idea with LAPGAN. Inspired by this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps. 
%%% Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear. 
Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs. The idea is adding symmetric generator and discriminator layers gradually for high-resolution image generation (Figure \ref{fig:archs-review} C). \textit{Compared with these strategies that train low-to-high resolution GANs stage-by-stage or progressively, our method has the advantage of leveraging mid-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. Particularly, using deep supervision \cite{lee2015deeply} in hierarchical convolutional layers provides short error paths and increases the discriminativeness of feature representations. 
\textit{Our hierarchically-nested adversarial objective is inspired by these families of deeply-supervised CNNs. }
%%%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.

@@

\subsection{Adversarial objective basics}
In brief, a GAN \cite{goodfellow2014generative} consists of a generator $G$ network and a discriminator $D$ network, which are playing an adversarial game to compete with each other. The discriminator is optimized to distinguish synthesized images from real images, meanwhile the generator is optimized to generate fake images to fool the discriminator. Concretely, the overall min-max optimization objective is defined as: 
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{V}(D, G, Y, \bm z),
\end{split}
\end{equation}
where $Y$ and $\bm z \sim \mathcal{N}(0,1)$ denote training images and random noises, respectively. 
%$G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$. 
$\mathcal{V}$ is the overall GAN objective, which usually takes the (cross-entropy loss) form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ or other variations \cite{lsgan,berthelot2017began}.

@@

\subsection{Hierarchical-nested adversarial objectives}
Numerous GAN methods have demonstrated ways to unite generators and discriminators for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
Our method actually explores a new dimension of playing this adversarial game along the depth of a generator (Figure \ref{fig:archs-review} D), which integrates additional hierarchical-nested  discriminators at intermediate layers of the generator. 
The proposed objectives act as regularizers to the hidden space of $\mathcal{G}$, which also offer a short path for better error signal flow and helps reduce the training instability.

The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4) with multiple resolution-growing side outputs:
%This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.  
\begin{equation}
\label{side}
X_1,..., X_s = \mathcal{G}(\bm t, \bm z), 
\end{equation}
where  $\bm t\sim p_{data}$ denotes a sentence embedding vector in the real training data distribution (generated by a pre-trained char RNN encoder). $\{X_1,...,X_{s-1}\}$ are resolution-growing images and $X_s$ is the final output with the highest resolution.

@@

For each side output $X_i$ from the generator, a distinct discriminator $D_i$ is associated to compete with it. Therefore, our full min-max objective is defined as 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{\mathcal{G}}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z), \\
  %\text{where} \;\;	 \mathcal{D} & =  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
\end{split}
\end{equation}
where $\mathcal{D}  =  \{D_1, ..., D_s\} $ and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ is a set of training images at multi-scales, $\{1,...,s\}$.
Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), which learn discriminative features in different contextual scales, respectively.

In principle, the lower-resolution side output is used to learn semantic consistent image structures (e.g. object sketches, colors, and background), and the subsequent higher-resolution side outputs are used to render fine-grained details. Since our method is trained in an end-to-end manner, the lower-resolution side outputs can fully enjoy the top-down knowledge from higher resolutions, such that we can observe consistent image structures and styles appear in both low and high resolutions.
The experiment demonstrates this advantage compared with StackGAN. 
% % According to our empirical observation, our design is able to reduce the model instability, especially at the early stage of the training.

%% %We present the following multi-purpose adversarial loss to support more effective generator training.

\subsection{Multi-purpose adversarial losses}
Our generator produces resolution-growing side outputs, which compose an image pyramid. 
We leverage this hierarchy property and allow adversarial losses to capture different statistics, with a goal to guarantee both semantic consistency and image fidelity.

In order to guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}. The discriminator is designed to take image-text pairs as inputs and be trained to differentiate two types of errors: a real image with mismatched text and a fake image with conditioned text.

The pair loss is designed to guarantee the global semantic consistency. However, there lacks an explicit loss that forces the discriminator to differentiate real images from fake images. And combining both tasks (generating realistic images and matching image styles with text) into one loss complicates the already challenging learning tasks. Moreover, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture the local fine-grained details (results are validated in experiments).
%As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
%However, this loss has two major weaknesses. First, there is no explicit loss that force the discriminator to differentiate real images from fake images. 
%Combining both tasks (generating realistic images and matching image with text) into one output further complicates the learning tasks, which is already challenging. 
%Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.  
In addition, as pointed in \cite{shrivastava2016learning}, a single global discriminator may over-emphasize certain biased local features and lead to artifacts.

To alleviate these issues and guarantee image fidelity, our solution is to add local adversarial image losses.
%as inspired by \cite{shrivastava2016learning}. 
%The insights are two folds:
%\begin{itemize}\vspace{-.1cm}
%\setlength\itemsep{-0.3em}
%\item Further forcing the generated samples to have only only global but also local similar statistics to real image patches, which is beneficial for rendering fine-grained details. 
%
%\item \textcolor{red}{Image loss without using paired text can be beneficial in the sense that it focus more on image information. The richness of discriminator supervision usually has advantages for generalization. } 
%\vspace{-.2cm}
%\end{itemize}
We expect the low-resolution discriminator to focus on global structures, while the high-resolution discriminator to focus  on local image details.
Each discriminator consists of two branches (see Section 3.4), one computes a single scalar value for the pair loss and another branch computes a $R{\times}R$ probability map. 
Each location differentiates whether an overlapping image patch is real or fake.
Through the pyramid of the size-growing side outputs, we control $R$ accordingly. Specifically, a larger $R$ value results in a smaller local range and finer focus of discriminators.
The local image adversarial loss can be implemented as an fully CNN \cite{shrivastava2016learning,zhu2017unpaired,isola2016image}.
Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on the generated images in the pyramid.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.49\textwidth]{figure/loss.pdf}
	\vspace{-.7cm}
	\caption{Given a set of images from the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and local image loss (outputting a $R{\times}R$ probability map to classify real or fake image patches). $R$ increases as the image size grows. }  \vspace{-.2cm}
	\label{fig:loss}
\end{figure}
